Embedding Dimension of Polyhedral Losses

### 2020-06-10 colt-20/embed-dim.tex
Updating for camera ready

\documentclass[anon]{colt2020} % Anonymized submission
% \documentclass{colt2020} % Include author names

@@

% Two authors with the same address
% \coltauthor{\Name{Author Name1} \Email{abc@sample.com}\and
%  \Name{Author Name2} \Email{xyz@sample.com}\\
%  \addr Address}

% Three or more authors with the same address:
 \coltauthor{\Name{Jessie Finocchiaro} \Email{jefi8453@colorado.edu}\\
  \Name{Rafael Frongillo} \Email{raf@colorado.edu}\\
  \Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
  \addr CU Boulder}

@@

\subsection{Related work}
\citet{zhang2004statistical,bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\citet{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.\jessiet{Do we want more of the canonical consistency papers?}
%, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.

@@

\begin{proposition} \label{prop:orderable-iff-path}
  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph\jessiet{tree?} where every vertex has either one or two neighbors.\jessiet{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?'' I don't see why this is wrong?}
\end{proposition}

@@

%% Bo: I think we can get away with no summary at the end.
%\paragraph{Conclusion.}
%\jessie{Not a fan, but a placeholder if we get too close to deadline.}
%In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
%While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
%In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
%In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
%
\newpage
% Acknowledgments---Will not appear in anonymized version
\acks{JF- Need that GRFP acknowledgement}

@@

\section{$1$-dimensional characterization omitted proofs}\label{app:1-dim}

\begin{proof}[Proof of Proposition~\ref{prop:orderable-iff-path}]
	$(\implies)$
	The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
	If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g.~\citep{lambert2009eliciting}).
	This yields a path for the intersection graph.

@@

We will make substantial use of the following general definition.
\begin{definition}\label{def:monotone-prop}
  A property $\Gamma:\simplex\to 2^\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
  \begin{enumerate}
  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
  \item For all $r < r'$, we have $a(r) \leq b(r) \leq a(r') \leq b(r')$ (component-wise).
  % \item For all $r,r'\in\R$ and $p\in\Gamma_{r'}\setminus\Gamma_r$, we have $b(r) \cdot p < 0 \implies r' > r$ and $a(r) \cdot p > 0 \implies r' < r$.
  \end{enumerate}
\end{definition}
\jessie{Can we explain in words the how orderable and monotone are different?}
\jessie{It is not immediately obvious that a property is orderable if and only if it is monotone.  Both definitions require an ordering on the reports, but it is not clear that the intersections of level sets on the relative interior of the simplex form hyperplanes from the definition of monotonicity.}

>>>>

\documentclass[final]{colt2020} % Anonymized submission
% \documentclass{colt2020} % Include author names

@@

% Two authors with the same address
% \coltauthor{\Name{Author Name1} \Email{abc@sample.com}\and
%  \Name{Author Name2} \Email{xyz@sample.com}\\
%  \addr Address}
\usepackage{thmtools, thm-restate}

% Three or more authors with the same address:
 \coltauthor{\Name{Jessie Finocchiaro} \Email{jessica.finocchiaro@colorado.edu}\\
  \Name{Rafael Frongillo} \Email{raf@colorado.edu}\\
  \Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
  \addr CU Boulder}

@@

\subsection{Related work}
\citet{zhang2004statistical,bartlett2006convexity} study when a convex, calibrated surrogate exists for a given discrete loss, and in a finite-outcome setting,~\citet{tewari2007consistency} show that calibration (Definition~\ref{def:calibration}) is necessary and sufficient for consistency.
%, meaning that there is a link mapping surrogate reports to discrete reports so that converging to the optimal prediction in the surrogate space implies the linked surrogate prediction converges to the optimal prediction for the original loss.

@@

\begin{restatable}{proposition}{orderableiffpath} \label{prop:orderable-iff-path}
  A finite property $\gamma$ is \emph{orderable} iff its intersection graph is a path, i.e. a connected graph where two nodes have degree $1$ and every other node has degree $2$.% neighbors, and two nodes have degree one.
  \jessiet{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?''}\jessiet{Added: and two nodes have degree one}
\end{restatable}

@@

%% Bo: I think we can get away with no summary at the end.
%\paragraph{Conclusion.}
%\jessie{Not a fan, but a placeholder if we get too close to deadline.}
%In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
%While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
%In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
%In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
%
\newpage
% Acknowledgments---Will not appear in anonymized version
\acks{Jessie Finocchiaro was funded by NSF Graduate Research Fellowship under grant \# DGE 1650115. \jessie{Others...?}}

@@

\section{$1$-dimensional characterization omitted proofs}\label{app:1-dim}
\orderableiffpath*
\begin{proof}[Proof of Proposition~\ref{prop:orderable-iff-path}]
	$(\implies)$
	The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
	If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g.~\citep{lambert2009eliciting}).
	This yields a path for the intersection graph.

@@

We will make substantial use of the following general definition.
\begin{definition}\label{def:monotone-prop}
  A property $\Gamma:\simplex\to 2^\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
  \begin{enumerate}
  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
  \item For all $r < r'$, we have $a(r) \leq b(r) \leq a(r') \leq b(r')$ (component-wise).
  % \item For all $r,r'\in\R$ and $p\in\Gamma_{r'}\setminus\Gamma_r$, we have $b(r) \cdot p < 0 \implies r' > r$ and $a(r) \cdot p > 0 \implies r' < r$.
  \end{enumerate}
\end{definition}

We have a property being orderable if and only if it is monotone since the maps $a$ and $b$ must define hyperplanes in the simplex in order for the ordering to be complete.
